### 2016-08-17 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the analysis and the answers

>>>>

  \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_x.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_t.pdf}
    \caption{ $A_{LU}$ ratio between $^{4}$He DVCS and free proton at $\phi = 
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:coh-alu-ratios}
    \end{figure}

 \begin{figure}[tbp]
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_Q2.pdf}
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_x.pdf}
    \centering
    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_t.pdf}
    \caption{ $A_{LU}$ ratio between bound proton and free proton at $\phi =  
    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
    \label{fig:incoh-alu-ratios}
    \end{figure}

### 2016-08-17 analysis-note-v2/results.tex
update the analysis and the answers

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.42]{fig_ch5/coh_alu_Q2_phi.png} 
\includegraphics[scale=0.42]{fig_ch5/coh_alu_xB_phi.png}
\includegraphics[scale=0.42]{fig_ch5/coh_alu_t_phi.png}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
quadratically, shown on the top of green error bars representing only the 
statistical uncertainties. The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_Q2_phi.png}
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_xB_phi.png}
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_t_phi.png}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ function.  
} \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[tpb]
\centering
\vspace{-0.2in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_Q2_90.png} \\
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_xB_90.png}\\ 
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_t_90.png} 
\caption{The $Q^{2}$ 
   (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
   of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
   the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\hspace{-0.5in}\includegraphics[scale=0.38]{fig_ch5/HA_Q2.png}
\hspace{-0.3in}\includegraphics[scale=0.38]{fig_ch5/HA_xB.png}
\centering \includegraphics[scale=0.38]{fig_ch5/HA_t.png}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_Q2.png}\\
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_xB.png}\\
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_t.png}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
$\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
middle), and $t$ (on the bottom). The black squares are our results, the 
green circles are the HERMES inclusive measurement \cite{HERMES_BSA} results. 
The blue and red curves are from an on-shell calculations from S. Liuti and K. Taneja 
\cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_ch5/coh_emc_Q2.png}\\
\includegraphics[scale=0.37]{fig_ch5/coh_emc_xB.png}\\
\includegraphics[scale=0.37]{fig_ch5/coh_emc_t.png}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
~\\

>>>>

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_Q2_phi.pdf} 
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_xB_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_coh_alu_t_phi.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
quadratically, shown on the top of green error bars representing only the 
statistical uncertainties. The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

@@

\begin{figure}[tpb]
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_Q2_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_xB_phi.pdf}
\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_t_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ function.  
} \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[tpb]
\centering
\vspace{-0.2in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} \\
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\ 
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \caption{The 
   $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of the 
   incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
   the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
   $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
   the colored curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\begin{figure}[h!]
\hspace{-0.5in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_Q2.pdf}
\hspace{-0.3in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_xB.pdf}
\centering \includegraphics[scale=0.38]{fig_updated/f_coh_cff_t.pdf}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_xB.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_t.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
$\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
middle), and $t$ (on the bottom). The black squares are our results, the 
green circles are the HERMES inclusive measurement \cite{HERMES_BSA} results. 
The blue and red curves are from an on-shell calculations from S. Liuti and K. Taneja 
\cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_t.pdf}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
~\\
